Niche complementarity among pollinators increases community-level plant reproductive success

### 2020-03-17 Network_structure_and_function.Rmd
reducing number of words to 5,000

Words in main text (excluding abstract, acknowledgements, references, table and figure legends): 5,272

@@

Pollinators provide key services to plants by facilitating pollen flow between individuals [@Garibaldi2013]. Records of declining trends for some pollinator species in some regions ([@Potts2010; @I.2019]) have led researchers to focus on the functional impacts of these changes in pollinator diversity, especially on the consequences for plant reproductive success [@Biesmeijer2006].

  Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain the differences observed (e.g., [@Bommarco2012]). Contrastingly, community-level analyses remain scarce [@Bennett2018]. Yet plants and pollinators do not interact in isolation, but rather are embedded within larger networks of interactions encompassing other plant and pollinator species [@Memmott2004a]. We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect interactions between species within one guild (e.g., plants) through their shared resources [@Carvalheiro2014; @Lazaro2014; @Mayfield2017; @Pauw2013; @Johnson2019]. Understanding how changes in pollinator diversity and interaction structure affect ecosystem functioning is thus a major challenge that requires attention.

  The few pollination studies that have analyzed the effects of changing pollinator diversity for reproductive success at the community level have done so using mainly experimental setups. As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found a positive effect of pollinator species diversity on seed set, but also an important effect of niche complementarity between pollinators, a measure of community structure [@Frund2013]. These findings show that not only the diversity of species present, but also the diversity of roles they play and the way in which a community is structured are determinant factors of ecosystem functions.

  Indeed, theoretical research has long suggested that the structure of multitrophic communities has an effect for ecosystem functioning (reviewed in [@Thompson2012]). This line of research, rooted in niche theory and revamped by food-web studies [@Godoy2018; @Macarthur1967; @May1972a; @Tilman1982], has greatly advanced theory, but the relationship between structure and function has seldom been tested using empirical data (but see [@Kaiser-Bunbury2017; @Poisot2013; @Lazaro2019]). Specifically, a major knowledge gap resides in understanding which aspects of structure determine which aspects of function [@Thompson2012]. This is because although a network perspective has promised to encapsulate complex ecological mechanisms occurring at the community level – such as indirect interactions [@Abrams1998; @Holt1977] or niche overlap [@Woodward2002]- less attention has been given to the ways in which these mechanisms relate to observed ecosystem processes [@Bluthgen2010a]. In contrast, we are now at a point where we understand some of the emergent patterns characterizing mutualistic interaction networks at the community level, especially in the case of pollination [@Bascompte2007a]. Amongst them is the prevalence of nested structures, i.e., arrangements where specialist species interact with a subset of the species that generalists interact with [@Bascompte2003]. Further, plant-pollinator interaction networks seem to exhibit a relatively high extent of complementary specialization at the community scale, which may be directly related to key ecosystem functions [@Bluthgen2011]. However, the mechanisms by which these attributes affect plant reproduction remain to be understood [@Winfree2013]. The time is thus ripe to explore the relationship between community structure and ecosystem functioning empirically, with special emphasis on the underlying ecological mechanisms that drive these relationships.

  Here, we present an empirical study linking pollinator visitation and plant reproductive success at the community level using empirical data on plant-pollinator interaction networks and plant reproductive success. To this end, we use a well-replicated dataset encompassing plant-pollinator interaction networks collected at 16 sites coupled with data on the reproductive success of 19 plant species recorded in Mediterranean shrub ecosystems. Our study focuses on understanding whether adding information on selected interaction network structure indices to previously used simple visitation metrics (e.g., the number and diversity of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success. In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the association between the position of a focal species within the larger network and its link to individual reproductive success, and (ii) at the site level, by evaluating how attributes that describe the whole site might affect average values of reproductive success for all species measured within one particular site. Specifically, our study focuses on how the interplay between the complementarity in plant species visited by different pollinators (i.e., the complementarity in the functions they perform) and the redundancy in this function relates to reproductive success. Plant reproductive success requires of the delivery of conspecific pollen and thus of a certain degree of niche complementarity [@Bluthgen2011]. Yet, greater values of redundancy in species functions (e.g., that provided by nested structures), are thought to promote species diversity [@Bastolla2009] and stability [@Thebault2010a] within plant-pollinator networks. At present, we do not know how either of these network characteristics affects the functions performed by pollinators.

  Our results suggest that models including information on simple visitation metrics alone are good in explaining the variability observed in reproductive success. However, insights into the mechanisms through which differences in pollinator diversity translate into changes in reproductive success require additional information on network structure, notably information on the complementarity between the functions performed and the niches occupied by different pollinator species. Specifically, we find a positive effect of increasing niche complementarity between pollinators on plant reproductive success.

@@

Our study was conducted in SW Spain within the area of influence of Doñana National Park, i.e., within the limits of the Natural Space of Doñana as defined by the local government (Junta de Andalucía, Fig. S1). All 16 sites were located within similar elevations (ranging from 50 to 150 m a.s.l.), similar habitat and soil types, and presented similar plant composition (plant mean Sørensen beta-diversity among sites = `r round(d.betadiv, 2)`), reducing potential confounding factors. Here, we surveyed 16 Mediterranean woodland patches with an average distance of 7 km between them (min= 3 km, max= 46.5 km). Each site was surveyed every two weeks for a total of 7 times during the flowering season of 2015 (from February to May) following a 100-m x 2 m transect for 30 mins. Along each transect, we identified all plant species and recorded all the floral visitors that landed on their flowers during each 30-min period. Only floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FPM and another expert entomologist (see acknowledgements). All surveys were done under similar weather conditions, avoiding windy or rainy days, during mornings and afternoons with the sampling order being established randomly. Within each transect every 10 m we surveyed a 2x2 m quadrant where the number of flowers per species were counted, i.e., 10 quadrats per transect which makes 40m2 of area surveyed overall.

@@

Within each site, we marked between 3 and `r max(f.inds$tot.inds)` individuals (mean $\pm$ SD: `r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`, Table S2) belonging to `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (mean $\pm$ SD:`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`, Table S2). For each individual, at the end of the season, we recorded fruit set (i.e. the proportion of flowers that set fruit), the average number of seeds per fruit and the average fruit and seed weight per fruit (`r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits subsampled, mean $\pm$ SD: `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`, Table S3). These last two variables show a strong correlation (Pearson correlation= 0.89), but we believe they provide complementary information. Our survey included a total of `r nlevels(f2$Plant.sp)` different totally or partially self-incompatible plant species that depend on pollinators to maximize their reproduction (Table S4) across our `r nlevels(f2$Site_ID)` sites. All plant species were shrubs selected to be common and widespread species. Individuals were selected depending on the presence of flowers during the sampling events. In addition to species-level values, we also calculated the average reproductive success at the site level. To that end, the values of reproductive success obtained at the species level were averaged per site.

@@

In order to evaluate the completeness of our sampling, we estimated the asymptotic number of species of plants, pollinators and interactions present [@Chao2009], a non-parametric estimator of species richness for abundance data. This estimator includes non-detected species and allowed us to calculate the proportion detected with our original sampling data. We used Chao 1 asymptotic species richness estimators [@Chao2009] and estimated the richness of pollinators, plants and plant–pollinator links accumulated as sampling effort increased up to 100% sampling coverage using package iNEXT [@Hsieh2016] within the R environment [@RDevelopmentCoreTeam2011]. We then extracted the values covered by our sampling.

  In order to analyse how differences in network structure between communities might affect plant reproductive success, we constructed quantitative plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling. We thus obtained one interaction network per site, representing the number of individuals of different pollinator species recorded visiting each different plant species. For each network, we then extracted a series of relevant network metrics at the species and site levels.

  In addition, we checked for potential spatial autocorrelation in our data by means of Mantel correlograms. Autocorrelation values were non-significant for all variables included in our analyses, except in the case of pollinator richness where we have a small but significant effect at small spatial scales (Fig. S2), and hence we treat each site as independent in our analysis.

@@

At the species level, we focused on attributes defining the position of a focal plant species within the larger community. As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap in terms of pollinators between a focal plant species and each of the other plant species in the community, which estimates the potential indirect interactions between different plant species through shared resources (in this case pollinators) and the potential for increased heterospecific pollen deposition [@Arceo-Gomez2019], and (ii) centrality, which depicts the importance of the role played by a plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness. 
 Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita overlap index, a measure of similarity between two sets of data [@Zhang2016]. As a measure of centrality, we used weighted closeness centrality, which represents the number of shortest paths going through a focal plant based on a unipartite projection of the bipartite plant-pollinator network using a weighted representation of the network [@Dormann2009]. With this method, links between plant species represent shared pollinator species.

@@

At the site level, we followed the same logic as the one presented at the species level. Thus, we also calculated two network metrics providing complementary non-redundant information. In this case we focused on a metric that measures the redundancy in the plants visited by different pollinators, nestedness, and another one, not correlated with the previous one, measuring the complementarity in the plant species visited by the different pollinator species, pollinator niche complementarity.

  Nestedness is the property by which specialists interact with a subset of the species that generalists interact with [@Bascompte2003]. Although there is an ongoing debate in the literature (e.g., [@James2012]), some theoretical studies have found that nested networks are more stable and resilient to perturbations because nestedness promotes a greater diversity by minimizing competition among species in a community [@Bastolla2009]. However, many network attributes vary with network size and complexity [@Bluthgen2006]. In the case of nestedness, we know it can be affected by network size and connectance [@Song2017a]. An approach that is often used to correct for this, is to use null models and to compare null-model corrected nestedness values across different networks. However, this approach has been shown to present the same issues, as z-scores also change with network size and connectance [@Song2017a]. We thus followed the advice provided by Song et al. (2017) by using a normalized value of the widely used nestedness metric NODF based on binary matrices [@Almeida-Neto2011], $NODF_c$. This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance and S is network size, calculated as $S = \sqrt(ncol(web)*nrow(web))$. $NODF_n$ is calculated as $NODF/max(NODF)$, which is independent of network size and thus comparable across different networks [@Song2017a]. To calculate max(NODF) we used a corrected version of the algorithm [@Simmons2019a] whenever possible. Results did not change qualitatively when using the uncorrected version of the algorithm for all sites as both are highly correlated (Spearman correlation = 0.94).

@@

To evaluate whether adding information on network structure improves our ability to explain differences in reproductive success - both at the species and the site level - we used generalized linear (GLMs) and generalized linear mixed models (GLMMs) respectively. In both cases (species and site-level models) we fit three types of models: (i) model 0, a null model with no explanatory variables,(ii) model 1, that only included simple visitation metrics and (iii) model 2 that additionally included information on network structure. These models are meant to be additive, so that the network metrics included are intended to complement rather than substitute the simple metrics traditionally used.

At the species level, response variables included fruit set analyzed using a binomial distribution and the average number of seeds per fruit, the average fruit and seed weight fitted using normal distributions. The number of seeds per fruit was centered and scaled (i.e., we subtracted column means and divided by standard deviation) to allow meaningful comparisons across species with contrasting life histories. As explanatory variables, model 1 included the number of pollinator species observed, and the visitation rate received by each plant species. Visitation rate was calculated as the total number of visits received by a plant species divided by the average number of flowers of that species found in the 10 2x2 m quadrats located every 10 m along the transect. In turn, model 2 added the two network attributes calculated at the species level: average plant niche overlap and centrality. For both models, we included plant species identity nested within site and site as random effects to account for the fact that several individuals of the same plant species were measured at each site.

	At the site level, response variables were the average reproductive success of all plants surveyed within a site (i.e., average fruit set analyzed using a binomial distribution, average number of seeds per fruit and average fruit and seed weight using a normal distribution). We thus had a single value per site and no random effects are needed. In this case, model 1 included total pollinator richness and total pollinator abundance (i.e. number of visits received by all plants within the community) as explanatory variables. Model 2, in turn, added information on network structure by including nestedness and pollinator niche complementarity.

  Average values of reproductive success at the site level can be driven to a large extent by a single plant species. Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” or evenness in reproductive success across the whole community. We therefore calculated the proportion of species with normalized (between 0 and 1) average fruit set values that were above the 50^th percentile as a measure of equity. As any selected threshold is arbitrary, we repeated this using the 25^th and 75^th percentile thresholds [@Byrnes2014]. We then used the same framework as that used for species and site-level analyses and fit the same models 0, 1 and 2 GLMs using equity in reproductive success as response variable and fitting a binomial distribution.

  In all cases, we used variance inflation factors to check for collinearity between explanatory variables. Additionally, we ran residual diagnostics to check if model assumptions were met and used the Akaike Information Criterion (AIC) to compare model performance and complexity. Whenever the difference between the AIC of the models was < 2 ($\Delta AIC<2$), we considered that all models were equally good [@Burnham2011]. In the case of mixed models, for comparison, models were fitted by maximum likelihood and then the best model was refitted using restricted maximum likelihood. All predictor variables were standardized prior to analysis. For every model we also calculate the R2 value using the approximation suggested for GLMMs when necessary [@Shinichi2017].

@@

  To test this, we ran a simple simulation in which the number of species considered increased at each step and for each step we re-calculated equity in reproductive success. Instead of drawing plant species randomly for each step, we tested all possible combinations for each plant number level and network, as the number of combinations is small (e.g. for n = 3 plant selected out of 6 there is only 20 possible combinations). Then, we tested if the relationship between equity in reproductive success and niche complementarity (given its importance in determining differences in reproductive success, see Results section) changes as a function of the number of plants considered within our simulated communities. To this end, for each level of species number considered, we randomly selected one of the generated equity values across each of the 16 communities and regressed these 16 values against our network level predictor and extracted the model slope estimates. We repeated this process 1,000 times and averaged all slope estimates. We expect that the more plants considered, the larger the resulting average estimates will be. Note that we only interpret the mean effects, as the variance among different plant number of species considered depends on the initial number of possible combinations.

@@

  Our sampling completeness analyses revealed that with our survey we were able to capture 17-54% of pollinator species (average = 35%), 43-100% for plant species (average = 80%) and 9-32% for plant-pollinator links (average = 20%), in line with that obtained with other studies (e.g., [@Chacoff2012], Fig. S3). Our values of sampling completeness were slightly smaller in the case of pollinators, probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity [@Nieto2014].

@@

At the species level, in the case of fruit set, our results showed that model 2 had the best fit to our data (lowest AIC value), and fixed  effects explained `r round(r2$Marginal[1], 2)*100`% of the variability observed (conditional R^2=`r round(r2$Conditional[1], 2)*100`%). In this case, we found a positive relationship between fruit set, visitation rate, and a network structure metric, the centrality of a focal plant within the overall network (Table 1, Fig. 1A, Fig. S4). However, in the case of the relative number of visits a single point seemed to be driving the relationship and removing this single point lead to a decrease in the importance of this variable (Fig. S5, Table S5).

@@

```
 For all other measures of reproductive success considered (i.e., fruit and seed weight), none of the models fitted showed a better fit than the null model.

@@

At the site level, in the case of fruit set and the number of seeds per fruit, we found that both model 1 and 2 were equally good in describing the differences observed when penalizing for model complexity (i.e.,$\Delta AIC<2$; [@Burnham2002a]). This suggests model 2 was a good model despite its added complexity, and actually shows a substantially better predictive ability than model 1 (R^2 = `r round(r2.m2, 2)` for model 2 versus `r round(r2.m1, 2)` for model 1 in the case of fruit set and R^2 = `r round(r2.m2.seed,2)` for model 2 versus `r round(r2.m1.seed, 2)` for model 1 in the case of the number of seeds per fruit) and therefore we will comment results for this model only. In particular, we found that both fruit set and the number of seeds per fruit were positively related to niche complementarity between pollinators (Tables 2, Fig. 2, Fig. S6). Additionally, we found a negative association between site-level pollinator richness and average fruit set (Table 2A, Fig. 2, Fig. S6).

@@

pltest <- ggplot(s.comm,  aes(x=species.poll.sc, y= restest)) +    
  geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
  stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +
  #ylim(0.3,0.9) +
  xlab("Pollinator richness") +      
  ylab("Fruit weight (g)") + theme_bw()  + #theme (legend.position= "none") +
  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))

@@

pltestb <- ggplot(s.comm2,  aes(x=species.poll.sc, y= restestb)) +    
  geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
  stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +
  #ylim(0.3,0.9) +
  xlab("Pollinator richness") +      
  ylab("Fruit weight (g)") + theme_bw()  + #theme (legend.position= "none") +
  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))

@@

FigureS7<-cowplot::plot_grid(pltest, pltest2, labels = c("A", "B"), nrow=1)

>>>>

Words in main text (excluding abstract, acknowledgements, references, table and figure legends): 4,997

@@

Pollinators provide key services to plants by facilitating pollen flow [@Garibaldi2013]. Declining trends for some pollinator species in some regions ([@Potts2010; @I.2019]) have led researchers to focus on the functional impacts of these changes in pollinator diversity, especially for plant reproductive success [@Biesmeijer2006].

  Many studies have evaluated reproductive success on individual plant species [@Albrecht2012; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species visiting a plant or the number of visits they perform) to explain the differences observed (e.g., [@Bommarco2012]). Contrastingly, community-level analyses remain scarce [@Bennett2018]. Yet plants and pollinators do not interact in isolation but are embedded within larger networks of interactions encompassing other plant and pollinator species [@Memmott2004a]. We are thus missing an important part of the picture, including direct interactions between the whole ensemble of plants and pollinators, but also indirect ones between species within one guild (e.g., plants) through their shared resources [@Carvalheiro2014; @Lazaro2014; @Mayfield2017; @Pauw2013; @Johnson2019]. Understanding how changes in pollinator diversity and community structure affect ecosystem functioning is thus a major challenge that requires attention.

  The few studies that have analyzed the effects of pollinator diversity on reproductive success at the community level have mainly used experimental setups. As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity, found a positive effect of pollinator species diversity on seed set, but also an important effect of niche complementarity between pollinators, a measure of community structure [@Frund2013]. These findings show that not only the diversity of species present, but also the diversity of roles they play and thus the way in which a community is structured are determinant factors of ecosystem functions.

  Indeed, theoretical research has long suggested that the structure of multitrophic communities has an effect for ecosystem functioning (reviewed in [@Thompson2012]). This line of research, rooted in niche theory and revamped by food-web studies [@Godoy2018; @Macarthur1967; @May1972a; @Tilman1982], has greatly advanced theory, but the relationship between structure and function has seldom been tested using empirical data (but see [@Kaiser-Bunbury2017; @Poisot2013; @Lazaro2019]). Specifically, a major knowledge gap resides in understanding which aspects of structure determine which aspects of function [@Thompson2012]. This is because although a network perspective has promised to encapsulate complex ecological mechanisms occurring at the community level – such as indirect interactions [@Abrams1998; @Holt1977] or niche overlap [@Woodward2002]- less attention has been given to the ways in which these mechanisms relate to observed ecosystem processes [@Bluthgen2010a]. We are now at a point where we understand some of the emergent patterns characterizing mutualistic interaction networks at the community level, especially in the case of pollination [@Bascompte2007a]. Amongst them is the prevalence of nested structures, i.e., arrangements where specialist species interact with a subset of the species that generalists interact with [@Bascompte2003]. Further, plant-pollinator interaction networks seem to exhibit a relatively high extent of complementary specialization at the community scale, which may be directly related to key ecosystem functions [@Bluthgen2011]. However, the mechanisms by which these attributes affect plant reproduction remain to be understood [@Winfree2013]. The time is thus ripe to explore the relationship between community structure and ecosystem functioning empirically, with special emphasis on the underlying ecological mechanisms that drive these relationships.

  Here, we present an empirical study linking pollinator visitation and plant reproductive success at the community level. We use a well-replicated dataset encompassing plant-pollinator interaction networks collected at 16 sites coupled with data on the reproductive success of 19 plant species recorded in Mediterranean shrub ecosystems. Our study focuses on understanding whether adding information on selected interaction network structure indices to previously used simple visitation metrics (e.g., the number and diversity of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success. In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the association between the position of a focal species within the larger network and its link to individual reproductive success, and (ii) at the site level, by evaluating how attributes that describe the whole site might affect average values of reproductive success for all species measured within one particular site. Specifically, our study focuses on how the interplay between the complementarity in plant species visited by different pollinators, and the redundancy in this function relate to reproductive success. Plant reproductive success requires of the delivery of conspecific pollen and thus of a certain degree of niche complementarity [@Bluthgen2011]. Yet, greater values of redundancy in species functions (e.g., that provided by nested structures), are thought to promote species diversity [@Bastolla2009] and stability [@Thebault2010a] within plant-pollinator networks. At present, we do not know how either of these network characteristics affects the functions performed by pollinators.

  Our results suggest that models including information on simple visitation metrics alone are able to explain differences in reproductive success. However, a mechanistic understanding requires additional information on network structure, notably information on the complementarity between the niches occupied by different pollinator species. Specifically, we find a positive effect of increasing niche complementarity between pollinators on plant reproductive success.

@@

Our study was conducted in SW Spain within the area of influence of Doñana National Park (Fig. S1). Sites were located within similar elevations (ranging from 50 to 150 m a.s.l.), similar habitat and soil types, and presented similar plant composition (plant mean Sørensen beta-diversity among sites = `r round(d.betadiv, 2)`), reducing potential confounding factors. We surveyed 16 Mediterranean woodland patches with an average distance of 7 km between them (min= 3 km, max= 46.5 km). Each site was surveyed every two weeks for a total of 7 times during the flowering season of 2015 (from February to May) following a 100-m x 2 m transect for 30 mins. Along each transect, we identified all plant species and recorded all the floral visitors that landed on their flowers. Only floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FPM and another expert entomologist (see acknowledgements). All surveys were done under similar weather conditions, avoiding windy or rainy days, during mornings and afternoons with the sampling order being established randomly. Within each transect every 10 m we surveyed a 2x2 m quadrant where the number of flowers per species were counted, i.e., 10 quadrats per transect which makes 40m2 of area surveyed overall.

@@

Within each site, we marked 3-`r max(f.inds$tot.inds)` individuals (mean $\pm$ SD: `r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`) belonging to `r min(tableS1$tot.sps)`-`r max(tableS1$tot.sps)` plant species (mean $\pm$ SD:`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`, Table S2). For each individual, at the end of the season, we recorded fruit set (i.e. the proportion of flowers that set fruit), the average number of seeds per fruit and the average fruit and seed weight per fruit (`r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits subsampled, mean $\pm$ SD: `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`, Table S3). These last two variables show a strong correlation (Pearson correlation= 0.89), and thus we only present results on fruit weight. Our survey included a total of `r nlevels(f2$Plant.sp)` different totally or partially self-incompatible plant species that depend on pollinators to maximize their reproduction (Table S4) across our `r nlevels(f2$Site_ID)` sites. All plant species were common and widespread shrubs. Individuals were selected depending on the presence of flowers during the sampling events. We also calculated the average reproductive success at the site level by averaging values of reproductive success obtained at the species level.

@@

To evaluate the sampling completeness, we estimated the asymptotic number of species of plants, pollinators and interactions present [@Chao2009], a non-parametric estimator of species richness for abundance data. This estimator includes non-detected species and allowed us to calculate the proportion detected with our original data. We used Chao 1 asymptotic species richness estimators [@Chao2009] and estimated the richness of pollinators, plants and plant–pollinator links accumulated as sampling effort increased up to 100% sampling coverage using package iNEXT [@Hsieh2016] within the R environment [@RDevelopmentCoreTeam2011]. We then extracted the values covered by our sampling.

  To evaluate differences in network structure between communities, we constructed quantitative plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling. We thus obtained one interaction network per site, representing the number of individuals of different pollinator species recorded visiting each different plant species. For each network, we extracted a series of relevant network metrics at the species and site levels.

  Additionally, we checked for spatial autocorrelation in our data using Mantel correlograms. Autocorrelation values were non-significant for all variables, except for pollinator richness where we have a small but significant effect at small spatial scales (Fig. S2). Hence, we treat each site as independent in our analysis.

@@

At the species level, we focused on attributes defining the position of a focal plant species within the larger community. As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap in terms of pollinators between a focal plant species and each of the other plant species in the community, which estimates the potential indirect interactions between plant species through shared resources (in this case pollinators) and the potential for increased heterospecific pollen deposition [@Arceo-Gomez2019], and (ii) centrality, which depicts the importance of the role played by a plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness. 
 Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita overlap index, a measure of similarity between two sets of data [@Zhang2016]. As a measure of centrality, we used weighted closeness centrality, which represents the number of shortest paths going through a focal plant based on a unipartite projection of the bipartite plant-pollinator network using a weighted representation of the network [@Dormann2009]. With this method, links between plant species represent shared pollinator species.

@@

At the site level, we followed the same logic as the one presented at the species level. We also calculated two network metrics providing complementary non-redundant information. In this case, we focused on nestedness, a measure of the redundancy in the plants visited by different pollinators, and pollinator niche complementarity, a measure of the complementarity in plant species visited by different pollinator species.

  Nestedness is the property by which specialists interact with a subset of the species that generalists interact with [@Bascompte2003]. Although there is an ongoing debate in the literature (e.g., [@James2012]), some theoretical studies have found that nested networks are more stable and resilient to perturbations because nestedness promotes a greater diversity by minimizing competition among species in a community [@Bastolla2009]. However, many network attributes vary with network size and complexity [@Bluthgen2006]. In the case of nestedness, we know it can be affected by network size and connectance [@Song2017a]. An approach that is often used to correct for this are null models, comparing null-model corrected nestedness values across different networks. However, this approach presents the same issues, as z-scores also change with network size and connectance [@Song2017a]. We thus used a normalized value of the widely used nestedness metric NODF based on binary matrices [@Almeida-Neto2011], $NODF_c$ [@Song2017a]. This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance and S is network size, calculated as $S = \sqrt(ncol(web)*nrow(web))$. $NODF_n$ is calculated as $NODF/max(NODF)$, which is independent of network size and thus comparable across different networks [@Song2017a]. To calculate max(NODF) we used a corrected version of the algorithm [@Simmons2019a] whenever possible. Results did not change qualitatively when using the uncorrected version of the algorithm for all sites as both are highly correlated (Spearman correlation = 0.94).

@@

To evaluate whether adding information on network structure improves our ability to explain differences in reproductive success - both at the species and the site level - we used generalized linear (GLMs) and generalized linear mixed models (GLMMs) respectively. In both cases we fit three types of models: (i) model 0, a null model with no explanatory variables,(ii) model 1, that only included simple visitation metrics and (iii) model 2 that additionally included information on network structure. These models are meant to be additive, so that the network metrics included are intended to complement rather than substitute the simple metrics traditionally used.

At the species level, response variables included fruit set analyzed using a binomial distribution and the average number of seeds per fruit, and the average fruit weight fitted using normal distributions. The number of seeds per fruit was centered and scaled (i.e., we subtracted column means and divided by standard deviation) to allow meaningful comparisons across species with contrasting life histories. As explanatory variables, model 1 included the number of pollinator species observed, and the visitation rate received by each plant species. Visitation rate was calculated as the total number of visits received by a plant species divided by the average number of flowers of that species found in the 10 2x2 m quadrats per transect. In turn, model 2 added the two network attributes calculated at the species level: average plant niche overlap and centrality. For both models, we included plant species identity nested within site and site as random effects to account for multiple individuals of the same plant species measured at each site.

	At the site level, response variables were the average reproductive success of all plants surveyed within a site (i.e., average fruit set analyzed using a binomial distribution, average number of seeds per fruit and average fruit weight using a normal distribution). We thus had a single value per site and no random effects are needed. Here, model 1 included total pollinator richness and total pollinator abundance (i.e. number of visits received by all plants within the community) as explanatory variables. Model 2, in turn, added information on network structure by including nestedness and pollinator niche complementarity.

  Average values of reproductive success at the site level can be driven by a single plant species. Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” or evenness in reproductive success across the whole community. We therefore calculated the proportion of species with normalized (between 0 and 1) average fruit set values that were above the 50^th percentile as a measure of equity. As any selected threshold is arbitrary, we repeated this using the 25^th and 75^th percentile thresholds [@Byrnes2014]. We then used the same framework as that used for species and site-level analyses and fit the same models 0, 1 and 2 using equity in reproductive success as response variable and fitting a binomial distribution.

  In all cases, we used variance inflation factors to check for collinearity between explanatory variables. Additionally, we ran residual diagnostics to check if model assumptions were met and used the Akaike Information Criterion (AIC) to compare model performance and complexity. Whenever the difference between the AIC of the models was < 2 ($\Delta AIC<2$), we considered all models equally good [@Burnham2011]. In the case of mixed models, for comparison, models were fitted by maximum likelihood and then the best model was refitted using restricted maximum likelihood. All predictor variables were standardized prior to analysis. For every model we also calculate the R2 value using the approximation suggested for GLMMs when necessary [@Shinichi2017].

@@

  To test this, we ran a simple simulation in which the number of species considered increased at each step and for each step we re-calculated equity in reproductive success. Instead of drawing plant species randomly for each step, we tested all possible combinations for each plant number level and network, as the number of combinations is small (e.g. for n = 3 plants selected out of 6 there are only 20 possible combinations). Then, we tested if the relationship between equity in reproductive success and niche complementarity (given its importance in determining differences in reproductive success, see Results section) changes as a function of the number of plants considered within our simulated communities. To this end, for each level of species number considered, we randomly selected one of the generated equity values across each of the 16 communities and regressed these 16 values against our network level predictor and extracted the model slope estimates. We repeated this process 1,000 times and averaged all slope estimates. We expect that the more plants considered, the larger the resulting average estimates will be. Note that we only interpret the mean effects, as the variance among different plant number of species considered depends on the initial number of possible combinations.

@@

  Our sampling completeness analyses revealed that our survey was able to capture 17-54% of pollinator species (average = 35%), 43-100% of plant species (average = 80%) and 9-32% of plant-pollinator links (average = 20%), in line with that obtained with other studies (e.g., [@Chacoff2012], Fig. S3). Our values of sampling completeness were slightly smaller in the case of pollinators, probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity [@Nieto2014].

@@

At the species level, in the case of fruit set, our results showed that model 2 had the best fit to our data (lowest AIC value), and fixed  effects explained `r round(r2$Marginal[1], 2)*100`% of the variability observed (conditional R^2=`r round(r2$Conditional[1], 2)*100`%). We found a positive relationship between fruit set, visitation rate, and a network structure metric, the centrality of a focal plant within the overall network (Table 1, Fig. 1A, Fig. S4). However, in the case of the relative number of visits a single point seemed to be driving the relationship and removing this single point lead to a decrease in the importance of this variable (Fig. S5, Table S5).

@@

```
 For fruit weight, none of the models fitted showed a better fit than the null model.

@@

At the site level, in the case of fruit set and the number of seeds per fruit, we found that both model 1 and 2 were equally good when penalizing for model complexity (i.e.,$\Delta AIC<2$; [@Burnham2002a]). This suggests model 2 was a good model despite its added complexity, and actually shows a substantially better predictive ability than model 1 (R^2 = `r round(r2.m2, 2)` for model 2 versus `r round(r2.m1, 2)` for model 1 in the case of fruit set and R^2 = `r round(r2.m2.seed,2)` for model 2 versus `r round(r2.m1.seed, 2)` for model 1 in the case of the number of seeds per fruit) and therefore we will comment results for this model only. Specifically, we found that both fruit set and the number of seeds per fruit were positively related to niche complementarity between pollinators (Tables 2, Fig. 2, Fig. S6). Additionally, we found a negative association between site-level pollinator richness and average fruit set (Table 2A, Fig. 2, Fig. S6).

@@

FigureS7 <- ggplot(s.comm,  aes(x=species.poll.sc, y= restest)) +    
  geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
  stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +
  #ylim(0.3,0.9) +
  xlab("Pollinator richness") +      
  ylab("Fruit weight (g)") + theme_bw()  + #theme (legend.position= "none") +
  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))

@@

FigureS8 <- ggplot(s.comm2,  aes(x=species.poll.sc, y= restestb)) +    
  geom_point(size=2.5, shape=21, color="black", fill="darkgrey") + 
  stat_smooth(method = 'lm', size=1, se=TRUE, color = "black", alpha=0.4) +
  #ylim(0.3,0.9) +
  xlab("Pollinator richness") +      
  ylab("Fruit weight (g)") + theme_bw()  + #theme (legend.position= "none") +
  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold"))

@@
